Probing the Deuteron at Very Large Internal Momenta

### 2020-10-23 PRL_UTILITIES_CODES/prl_wordcount/ms_withcites.tex
updated

have been compared to the high momentum part of theoretical deuteron momentum distributions \cite{PhysRevLett.97.162504,PhysRevLett.113.022501,PhysRevLett.122.172502,PhysRevLett.124.212501}.

@@

%\indent The kinematics of the recoiling neutron was reconstructed using energy-momentum conservation. The recoil momentum is defined as $\vec{p_{\mathrm{r}}} = \vec{q} - \vec{p_{\mathrm{f}}}$,
%and the nuclear binding (or ``missing'') energy as $E_{\mathrm{m}} = \omega - T_{p} - T_{\mathrm{r}}$, where $\vec{p_{\mathrm{f}}}$ is the final proton momentum, $\vec{q}$ is the
%3-momentum transfer and $T_{p}$ is the final proton kinetic energy. The recoil particle kinetic energy, $T_{\mathrm{r}}$, is calculated from the electron and proton
%4-momentum vectors assuming an exclusive three-body final state with a recoiling neutron.\\

@@

($E_{\mathrm{f}}, p_{\mathrm{f}}$) are the final proton energy and momentum, respectively, $f_{\mathrm{rec}}$ %\equiv \frac{2p_{\mathrm{f}}^{2}E_{\mathrm{r}}}{2p_{\mathrm{f}}^{2}E_{\mathrm{r}} - (q^{2} - (p_{\mathrm{f}}^{2} + p_{\mathrm{r}}^{2}))E_{\mathrm{f}}}$

@@

For the two highest momentum settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the reduced cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$. The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (red square). %The good agreement between the Hall A and C data at lower $p_{\mathrm{r}}$ gives us confidence in the measurements made at higher missing momentum settings for which no previous data exist.

@@

%----REMOVED ON 10/14/2020----------
%The MS calculations used the FF parametrization of Ref. \cite{PhysRevC.70.068202} while the JML calculations used the conventional dipole parametrization for
%the proton and neutron magnetic FF, the Galster \cite{Galster:1971} parametrization
%for the neutron electric FF, and the results from the Hall A experiment of Ref. \cite{PhysRevLett.88.092301} for the proton electric FF parametrization.
%The JVO calculations used two different FF parametrizations (GKex05 \cite{PhysRevC.66.045501}, AMT \cite{PhysRevC.76.035205}) where a
%difference of $\sim5.8-6.6 \%$ was found between the respective
%JVO reduced cross sections. Figure \ref{fig:fig1} shows the results using only the GKex05 parametrization. \\

@@

%---include references that are not mentioned in the main text
%---but are included in the supplemental material
%---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.
%\nocite{COSY}
\nocite{barlow2002systematic}
\nocite{barlow2017}

\end{document}
\bibliography{ms}

>>>>

have been compared to the high momentum part of theoretical deuteron momentum distributions.

@@

@@

($E_{\mathrm{f}}, p_{\mathrm{f}}$) are the final proton energy and momentum, respectively, $f_{\mathrm{rec}}$ 

@@

For the two highest momentum settings ($p_{\mathrm{r}}=580, 750$ MeV/c), a weighted average of the reduced cross sections were taken in the overlapping regions of $p_{\mathrm{r}}$. The results from the previous experiment \cite{PhysRevLett.107.262501} at a $Q^{2}=3.5\pm0.25$ (GeV/c)$^{2}$ are plotted as well (red square). 

@@

@@

%---include references that are not mentioned in the main text
%---but are included in the supplemental material
%---cite supp. material as follows:  (See Supplemental Material) after description of the topic being discussed.

\end{document}
\nocite{barlow2002systematic}
\nocite{barlow2017}

\bibliography{ms}
